### 2017-11-14 submission/supplemental.Rmd
remove unused table legends
add Will's supplemental suggestions

colnames(table_s1) <- c("F statistic", "R2", "P-value", "Study", "Adenoma n", "Control n")

@@

colnames(table_s2) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma n", "Control n")

@@

colnames(table_s3) <- c("F statistic", "R2", "P-value", "Study", "Adenoma n", "Control n")

@@

colnames(table_s4) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma n", "Control n")

@@

\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

**Table S2: Summary of Common OTUs for All Diagnosis Groups**

\footnotesize

```{r supplemental_table, echo=FALSE, message=FALSE, warning=FALSE}

```
\normalsize
\newpage

**Table S5: Summary of mtry ranges used for the treatment and diagnosis models**

\footnotesize

```{r supplemental_table6, echo=FALSE, message=FALSE, warning=FALSE}

```
\normalsize

>>>>

colnames(table_s1) <- c("F statistic", "R2", "P-value", "Study", "Adenoma (n)", "Control (n)")

@@

colnames(table_s2) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma (n)", "Control (n)")

@@

colnames(table_s3) <- c("F statistic", "R2", "P-value", "Study", "Adenoma (n)", "Control (n)")

@@

colnames(table_s4) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma (n)", "Control (n)")

@@
